---
title: "Experiment 1: Effect of First Insight"
output: html_document
date: "2023-06-15"
---

```{r imports, include=FALSE}
library(readr)
library(lme4)
```

```{r read data}
push_data <- read_csv("data/insight_push_data_coded.csv")
switch_data <- read_csv("data/insight_switch_data_coded.csv")
```

## Linear Mixed Effects Modeling
Fixed effects are as follows:

1. `trial_num`: the order in which the current trial was presented (0 to 7)

2. `insight`: whether or not the participant has previously successfully solved a push grid of the same type (-0.5 if false, 0.5 if true)

In order to assess whether the key term of interest (`insight`) is significant, we will perform model comparison of the following models using the anova function in R and use the p-value associated with the chi-square test.  

```{r exp}
push_data$insight <- 0
  for (i in unique(push_data$userid)) {
    idx_first_one <- which(push_data$userid == i & push_data$score_dif == 1)[1]
    if (!is.na(idx_first_one)) {
      push_data$insight[push_data$userid == i & seq_along(push_data$userid) > idx_first_one] <- 1
    }
  }
#push_data$trial <- push_data$trial - 1 

switch_data$insight <- 0
  for (i in unique(switch_data$userid)) {
    idx_first_one <- which(switch_data$userid == i & switch_data$score_dif == 1)[1]
    if (!is.na(idx_first_one)) {
      switch_data$insight[switch_data$userid == i & seq_along(switch_data$userid) > idx_first_one] <- 1
    }
  }
#switch_data$trial <- switch_data$trial - 1 


model1_p <- lmer(score_dif ~ (1|userid), data = push_data)
model2a_p <- lmer(score_dif ~ insight + (1|userid), data = push_data)
model2b_p <- lmer(score_dif ~ trial + (1|userid), data = push_data)
model3_p <- lmer(score_dif ~ insight + trial + (1|userid), data = push_data)
anova(model1_p, model2b_p, model3_p)
model3_p

model1_s <- lmer(score_dif ~ (1|userid), data = switch_data)
model2a_s <- lmer(score_dif ~ insight + (1|userid), data = switch_data)
model2b_s <- lmer(score_dif ~ trial + (1|userid), data = switch_data)
model3_s <- lmer(score_dif ~ insight + trial + (1|userid), data = switch_data)
anova(model1_s, model2b_s, model3_s)
model3_s
```

```{r emmeans}
library(emmeans)
emmeans(model3_p,specs = "insight")
emmeans(model3_s,specs = "insight")
```

```{r exploratory}

scale_this <- function(x){
  (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE)
}

switch_data$gridtype <- -0.5
push_data$gridtype <- 0.5

all_data <- rbind(switch_data, push_data)
all_data$insight <- all_data$insight - 0.5
all_data$trial <- scale_this(all_data$trial)
all_data$push_x_trial <- all_data$gridtype * all_data$trial
all_data$push_x_insight <- all_data$gridtype * all_data$insight
all_data$push <- all_data$gridtype

model1 <- lmer(score_dif ~ insight + trial + push + push_x_trial + (push|userid), data = all_data)
model2 <- lmer(score_dif ~ insight + trial + push + push_x_trial + push_x_insight + (push|userid), data = all_data)
anova(model1,model2)

```

