---
title: "Experiment 1 (Time Pressure/Delay Manipulation) "
output: html_document
---

```{r imports, include=FALSE}
library(readr)
library(lme4)
```

```{r read data}
data <- read_csv("data/time_pressure_data_coded.csv")
```

## Linear Mixed Effects Modeling
Fixed effects are as follows:

1. `time_delay`: the assigned time condition (0.5 if delay, -0.5 if pressure)

2. `in_distrib`: whether the grid belongs to a class seen in training (0.5 if in distrib, -0.5 if novel class)

3. `push`: differentiates between push and switch in the out of distribution cases (0 if in_distrib, 0.5 if grid belongs to must-push, -0.5 if grid belongs to must-switch)

4. `time_x_distrib`: interaction between in_distrib and time_delay

5. `time_x_push`: interaction between time_delay and push


In order to assess whether the key interactions of interest (`time_x_distrib` and `time_x_push`) is significant, we perform a series of model comparisons building up from the null model. `in_distrib` and `time_x_distrib` are dropped below as `model_3` and `model_5` are not preferred with `P<0.05`

```{r model comparisons}
model_1 <- lmer(score_dif ~ (in_distrib|user_id) + (time_constraint|grid_num), data = data)
model_2 <- lmer(score_dif ~ time_constraint  +  (in_distrib|user_id) + (time_constraint|grid_num), data = data)
anova(model_1, model_2)

model_3 <- lmer(score_dif ~ time_constraint + in_distrib + (in_distrib|user_id) + (time_constraint|grid_num), data = data, control = lmerControl(optimizer ="Nelder_Mead"))
anova(model_2, model_3)

model_4 <- lmer(score_dif ~ time_constraint + push + (in_distrib|user_id) + (time_constraint|grid_num), data = data)
anova(model_2, model_4)

model_5 <- lmer(score_dif ~ time_constraint + push + time_x_distrib +  (in_distrib|user_id) + (time_constraint|grid_num), data = data)
anova(model_4, model_5)

model_6 <- lmer(score_dif ~ time_constraint + push + time_x_push + (in_distrib|user_id) + (time_constraint|grid_num), data = data)
anova(model_4, model_6)

model_6
```
SI analysis, not pre-registered
```{r}
data_coded_pushswitch <- read_csv("data/time_pressure_data_coded_pushswitchonly.csv")
model_1s <- lmer(score_dif ~ (push|user_id) + (time_constraint|grid_num), data = data_coded_pushswitch)
model_2s <- lmer(score_dif ~ time_constraint + (push|user_id) + (time_constraint|grid_num), data = data_coded_pushswitch)
model_3s <- lmer(score_dif ~ time_constraint + push + (push|user_id) + (time_constraint|grid_num), data = data_coded_pushswitch)
model_4s <- lmer(score_dif ~ time_constraint + push + time_x_push + (push|user_id) + (time_constraint|grid_num), data = data_coded_pushswitch)
anova(model_2s, model_1s)
anova(model_3s, model_2s)
anova(model_4s, model_3s)
```



