---
title: "Experiment 3 (Training/No Training Manipulation)"
output: html_document
---

```{r imports, include=FALSE}
library(readr)
library(lme4)
```

```{r read data}
data <- read_csv("data/training_data_coded.csv")
```

## Linear Mixed Effects Modeling
Fixed effects are as follows: 

1. `train_group`: the assigned training condition (0.5 if training, -0.5 if no training)

2. `push`: differentiates between push type grids and the matched switch control (0.5 for must push, -0.5 for must switch) 

3. `train_x_push`: interaction between push and train_group 


In order to assess whether the key interaction of interest (`train_x_push`) is significant, we will perform model comparison using the `anova` function in R for the following models.

```{r models}
model_1 <- lmer(score_dif ~ push + (push|user_id) + (train|grid_num), data = data)
model_2 <- lmer(score_dif ~ train + (push|user_id) + (train|grid_num), data = data)
model_3 <- lmer(score_dif ~ train + push + (push|user_id) + (train|grid_num), data = data)
full_model <- lmer(score_dif ~ train + push + train_x_push + (push|user_id) + (train|grid_num), data = data)
summary(full_model)
```

```{r anovas}
anova(model_1, model_3)
anova(model_2, model_3)
anova(model_3, full_model)
```
